
\section{Experience}

\outerlist{

\entrybig
	{\textbf{Prisma} (\href{https://prisma.io}{prisma.io})}{Berlin, DE}
	{Software Engineer (Rust)}{Feb 2019\textendash}
\innerlist{

	\entry{Bootstrapped Prisma from Scala to Rust, bringing the Scala devs up to speed with the new language.}
    \entry{Wrote big parts of the Rust engines \cite{prismaEngines}}.
    \entry{Design, implementation \cite{tiberiusSource} and documentation \cite{tiberiusDocs} of a low level, asynchronous and runtime-independent Microsoft SQL Server library for Rust.}
    \entry{Discovery \cite{multiSchemaDiscovery} and design \cite{multiSchemaProposal} of the multi-schema product.}
    \entry{Design, implementation \cite{quaintSource} and documentation \cite{quaintDocs} of an SQL query builder and connector library for Rust.}
    \entry{Design \cite{postgresIndexProposal} and implementation \cite{postgresIndexImplementation} of PostreSQL special index types.}
    \entry{Implementation \cite{mongoIntrospectionImplementation} of MongoDB schema introspection.}
    \entry{Implementation \cite{postgresExtensionsImplementation} of PostgreSQL extensions in the Prisma Schema Language, introspection and migrations.}
    \entry{Re-design and organization of SQL introspection codebase \cite{sqlIntrospection}.}

}

\entrybig
        {\textbf{360dialog} (\href{https://www.360dialog.com/}{www.360dialog.com})}{Berlin, DE}
	{Senior Software Engineer (Rust, Clojure, Scala, Lua, C++)}{Apr 2016\textendash Sep 2018}
\innerlist{

    \entry{Design and implementation of push notification service \cite{xorcNotificationsImplementation} sending large amount of notifications to Apple's \cite{a2Implementation}, Google's \cite{fcmImplementation} and Web Push \cite{webPushImplementation} platforms in Rust.}

    \entry{Design and implementation of a RESTful API for campaign management, where customers could upload and transpile campaigns \cite{xorcGatewayImplementation}.}

    \entry{Maintaining and extending an in-house rule engine and virtual machine to execute campaign programs for millions of users. The system allows a custom program to be executed for every user and is written with C++ and Lua.}

    \entry{Maintaining and extending a code generator to create campaigns for the rule engine to run using Clojure. Handled a complete refactoring of the library and extended it to handle more use cases.}
}

%\pagebreak

\entrybig
        {\textbf{Fyber} (\href{https://www.fyber.com/}{www.fyber.com})}{Berlin, DE}
	{Senior Software Engineer (Ruby, Scala)}{Sep 2011\textendash Mar 2016}
\innerlist{
    \entry{Rewrote several parts of an advertisement service with Scala, including a high traffic tracker service and publisher callback system.}

    \entry{Designed and Implemented a statistics service and library with ZeroMQ, Ruby and Exasol.}

    \entry{Part of a core team to build a new backend infrastructure, implementing the ZeroMQ and Ruby based service from scratch.}
}

\entrybig
        {\textbf{Different Software Development Positions}}{Helsinki, FI}
	{Software Engineer (Ruby, C\#, Delphi, C++, Python, VBA)}{Jun 2006\textendash Sep 2011}
\innerlist{
    \entry{Companies, such as \href{https://www.corob.com/}{CPS Color}, \href{https://www.advania.fi/uutiset/meteoriitti}{Sininen meteoriitti}, \href{https://digia.com/}{Digia}}
}

}
